### 2021-01-29 research project/sections/Introduction.tex
rp work

The value of $\pi$ has been researched for many years, although under different names,
and the amount of different approaches to reach the value is large. The value has been 
found through many processes, be it analytically, the most popular, geometrically, or through 
more obscure or convoluted methods, such as the possibility to approximate the value using 
physics from billiards. \cite{galperin_2003}

>>>>

The value of $\pi$ has been researched for many years, although under different names,
and the amount of different approaches to reach the value is large. The value has been 
found through many processes, be it analytically, the most popular, geometrically, or through 
more obscure or convoluted methods, such as the possibility to approximate the value using 
physics akin to those from a simple game of billiards. \cite{galperin_2003}
